Bioverse: Origins of Life

### 2023-09-09 src/tex/ms.tex
add planet radius requirement

\subsection{Habitable Zone}
All Origins of Life scenarios considered here require water as a solvent; we thus consider only planets that may sustain liquid water on their surface.
Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the habitable zone $a_\mathrm{inner}$ and $a_\mathrm{outer}$.

>>>>

\subsection{Considered planets and their orbits}
All Origins of Life scenarios considered here require water as a solvent; we thus consider only rocky planets that may sustain liquid water on their surface.
Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the habitable zone $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as ``exo-Earth candidates'' all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.
